Guarded Recursion in Agda via Sized Types

### 2019-01-13 code-oneclock-paper/latex/paper.tex
Fixed running title
More elegant solution to make LiPiCS work with agda.sty
Added orcid

\titlerunning{Guarded Recursive Type Theory via Sized Types}%optional, please use if title is longer than one line

@@

\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{[orcid]}{}

@@

\usepackage{agda}

@@

% New commands for Agda inline code
\newcommand{\D}{\AgdaDatatype}
\newcommand{\IC}{\AgdaInductiveConstructor}
\newcommand{\F}{\AgdaFunction}
\newcommand{\Ar}{\AgdaArgument}
\newcommand{\Fi}{\AgdaField}
\newcommand{\AgdaUnderscore}{\_}

>>>>

@@

\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}

@@

\usepackage[noinputencodingsetup]{agda}

@@

% New commands for Agda inline code
\newcommand{\D}{\AgdaDatatype}
\newcommand{\IC}{\AgdaInductiveConstructor}
\newcommand{\F}{\AgdaFunction}
\newcommand{\Ar}{\AgdaArgument}
\newcommand{\Fi}{\AgdaField}
